---
title: "Research Proposal: Social Capital and Crime in Germany"
author: "Daniel Salgado Moreno and Lars Wehwald"
date: "23 October 2015"
output: pdf_document
---
pkgs <- c('dplyr', 'ggplot2')

repmis::LoadandCite(pkgs, file = 'RpackageCitations.bib')

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction and theory 
Most of crime studies are based on the rational choice assumptions of legal and criminal returns and the importnace of deterrence to reduce criminal behaviours (G. Backer, 2002). However, less has been writen about the relevance of social interactions explaining criminal behaviours. Some literature, though, has focused on the relationship between violent crimes and social capital. Lederman et al. (2002) identified that the prevalence of trust on community members has an effect on violent crimes and that the social cohesion through participation and membership in community oranisations only impact violent crime levels depending on the typ of religious and social organisation engaged. Additionally, Hanslaimer (2014) showed that atruism has a general negative effect on violent crimes, but other indicators of social capital only proved to be related to other types of high impact crime and not to violent crime. Hence, we are interested in responding to the question: How do social networks and bonds in a given community determine the level of violent crime? 
Social capital can be summerised as the links, shared values, and understandings in society that enable individuals and groups to trust each other and so work as a group (OECD). The concept of social capital gained importnace after Robert Putnam used it to describe the anomic state of the American society at the begining of the 21st century (Putnam, 2001). He argued that a decrease in community linkages that once held societies together and eged [WHAT DOES EGED MEAN?] to one another, translates in a loss of social capital (Putnam, 2001).
Additionally, we expect to observe that in societies with anomic and disorganization symptoms there are lower levels of social capital. Within this societies, groups and member interactions find themselves in a disruptive phase, damaging social bonds, norms, values, understandings and commitment. Environments where people lack a strong moral order lead to individual memebers to behave more egoistically therefore diminishing social capital. Disintegration of memebers of the community weakens social cohesion and promotes individualism that end in `machiavellian' competition, fostering feelings of stattus insequirity. Moreover, certan social milieus tend to be more vulnerable and respond therefore with violence. In addition, social capital provides means for informal punishment within a given community. Therefore more social capital leads to more abiding to social norms. In contrast communities that lack of social capital can merely punish norm diverging behaviour informally to a lesser extend and therefore are expected to have a higher crime rate.
With new data available for crime statistics for the years 2013 and 2014 at the districts' level in Germany it is relavant to study the incidence of high impact crimes and its relation to social capital formation. 
Results might be meaningful as rational for public intervention using crime reduction strategies that help build-up social capital at the community level (e.g. funding of sport clubs, gathering community, subsidies for staying in a community), instead of more aggresive interventionist policing strategies. Strategies that are less police intensive might have higher public support and might be seen as more legitimate. Social engagement at the local level might also help increase trust levels across community memebers and encorage more altruistic behaviours among them. Furthermore, social capital investment might be more cost-efficient compared to more aggresive policing tactics, which effects tend to be percieved only in the more immidiate time, whereas social capital investments and their effects might strech out for longer time.

## Methodology and analysis 
In order to answer the research question, we will apply a linear regression model. A binominal or multinominal regression model does not qualify, since we have a continuous, interval level dependent variable. Since our data only covers two time periods (t=2) we intend to use pooled OLS regressions. We thereby might run the risk to violate OLS assumptions when the values for a districts from one time period are correlated with the observation for this district at the other time period - assuming that the envirnomnent remains rather constant and districts with higher crime rates will also experience higher crime rates in the next period. Therefore we need to check statistically, whether our measured estimators are unbiased and efficient (e.g. comparing the results to a panel regression model, dummy for time period, heteroskedasticity). 

## Data
Our dependent variable crime rate can be obtained from the German Federal Police's crime statistic ("Polizeiliche Kriminalstatistik" PKS) for the years 2013 and 2014 on a district level ("Kreis"). This data is also disaggregated regarding the type of crime. This number, however, is missing the dark figure of crime - the unreported number of crime in this area. Different methods exist to assess the dark figure of crime, but it is difficult to assess their reliability. Hence, depending on the type of crime, the reported numbers might contain a structural bias, i.e. some types of crime are reported at a different rate than others (e.g. when insurance companies require individual reporting). Since we focus on crimes that disrupt the social community, we expect a high level of reporting and this reporting to be consistenly high across different types of disruptive crimes. It is possible to focus on one type of crime for our dependent variable, but also to construct a dependent variable summarising different types of crime. The latter approach might prove util, since this provides greater variance in the dependent variable. 
We want to measure different dimensions of our independent variable social capital. We beginn with a measurement for the networks and links dimension. This dimension highlights the importance of social bonds and meeting points in a community. We attempt to operationalise this dimension with indicators of marriages and migration. The indicator marriaged couples as a percentage of the population captures the notion that enhanced social ties increase the social capital of a community. Nevertheless this measure might be unreliable, since other forms of cohabitation (that are not measured by official statistics) can generate enhanced social links. In addition we might capture a different underlying concept (e.g. the role of tradition in a region) that is correlated with our dependent variable through a different causal mechanism. The other indicator, migration, aims at capturing the fluctuation of a region with other regions in Germany or with other nations. Since social capital requires time to build up, we expect higher crime rates in areas with high fluctuations.
Moreover we need distric level data for other variables to control for local heterogeneity. This data is provided by the German statistical bureau. We want to control for factors that influence the rational choice for committing a crime. First, unemployment changes the opportunity costs of punishment, i.e. imprisonment. Second, the level of income: high income reduces the punishment felt by individuals for minor charges (monetary penalty), but has no predetermined impact on the impact of inprisonment. In addition we want to control for a district's composition in age (younger persons are found to be more involved in crimes), gender (men are found to be more related to crimes), population size (i.e. more people, more expected crimes) and population density (as a proxy for urbanisation). As for now, we expect to obtain measures for some variables only for 2013. It needs to be determined, whether the fluctuation of the variable before 2013 allows to assume indentical values for 2014. 
On order to conduct the analysis, we need to merge the different datasets. We will use a combination of a unique identifier for the district ("Gemeindeschlüssel") and a year indicator (2013 or 2014). 

```{r SummaryData, echo=FALSE, message=FALSE}
# Loading required packages 
library("rio")
library("dplyr")
library("tidyr")

# Scrapping the data
URL_PKS_Kreise_13_14 <- "http://www.bka.de/SharedDocs/Downloads/DE/Publikationen/PolizeilicheKriminalstatistik/2014/BKATabellen/FaelleLaenderKreiseStaedte/tb01__FaelleGrundtabelleKreiseFallentwicklung__csv,templateId=raw,property=publicationFile.csv/tb01__FaelleGrundtabelleKreiseFallentwicklung__csv.csv"
PKS_Kreise_13_14 <- read.csv(URL_PKS_Kreise_13_14, sep=";")
rm(URL_PKS_Kreise_13_14)

# Delete (for now) unimportant variables
PKS_Kreise_13_14 <- PKS_Kreise_13_14[,-c(1, 4, 7:15)]

# Renaming manually 
NameofVariables <- c("Straftat", "Gemeindeschlüssel", "2014 - erfasste Fälle", "2013 - erfasste Fälle")
names(PKS_Kreise_13_14) <- NameofVariables 
rm(NameofVariables)

# Delete the first row (before name of variable)
PKS_Kreise_13_14 <- PKS_Kreise_13_14[-c(1),]

# Rearranging data
PKS_Kreise_13_14 <- PKS_Kreise_13_14[c(2,1,4,3)]

# Splitting the data
PKS_Kreise_13 <- PKS_Kreise_13_14[,c(1,2,3)]
PKS_Kreise_14 <- PKS_Kreise_13_14[,c(1,2,4)]
rm(PKS_Kreise_13_14)

# Spread data
PKS_Kreise_13_spread <- spread(PKS_Kreise_13, "Straftat", "2013 - erfasste Fälle")
PKS_Kreise_14_spread <- spread(PKS_Kreise_14, "Straftat", "2014 - erfasste Fälle")
rm(PKS_Kreise_13)
rm(PKS_Kreise_14)

# Adding year variable 
year13 <- 2013
PKS_Kreise_13_spread <- cbind(PKS_Kreise_13_spread, year13)
rm(year13)

year14 <- 2014
PKS_Kreise_14_spread <- cbind(PKS_Kreise_14_spread, year14)
rm(year14)

# Removing variables (crimes) not relevant to analysis
PKS_Kreise_13_spread <- PKS_Kreise_13_spread[,-c(3,4,5,6,11,12,13,14,15,16,17,18)]
PKS_Kreise_14_spread <- PKS_Kreise_14_spread[,-c(3,4,5,6,11,12,13,14,15,16,17,18)]

# Translation of variable names into English
NameofVariables <- c("district", "bodily harm", "dangerous bodily harm", "violent crime", "murder and manslaughter", "robbery", "year")
names(PKS_Kreise_13_spread) <- NameofVariables 
names(PKS_Kreise_14_spread) <- NameofVariables 
rm(NameofVariables)

# Changing the class of variables
class(PKS_Kreise_13_spread$district) <- "numeric"
class(PKS_Kreise_13_spread$`bodily harm`) <- "numeric"
class(PKS_Kreise_13_spread$`dangerous bodily harm`) <- "numeric"
class(PKS_Kreise_13_spread$`violent crime`) <- "numeric"
class(PKS_Kreise_13_spread$`murder and manslaughter`) <- "numeric"
class(PKS_Kreise_13_spread$robbery) <- "numeric"
class(PKS_Kreise_13_spread$year) <- "numeric"

class(PKS_Kreise_14_spread$district) <- "numeric"
class(PKS_Kreise_14_spread$`bodily harm`) <- "numeric"
class(PKS_Kreise_14_spread$`dangerous bodily harm`) <- "numeric"
class(PKS_Kreise_14_spread$`violent crime`) <- "numeric"
class(PKS_Kreise_14_spread$`murder and manslaughter`) <- "numeric"
class(PKS_Kreise_14_spread$robbery) <- "numeric"
class(PKS_Kreise_14_spread$year) <- "numeric"

# Summarising data
title1 <- "These are the summary statistics for the year 2013"
print(title1)
summary(PKS_Kreise_13_spread[,-c(1,7)])
rm(title1)

title2 <- "These are the summary statistics for the year 2014"
print(title2)
summary(PKS_Kreise_14_spread[,-c(1,7)])
rm(title2)

```

## Conclusion 
We expect to confirm our hypothesis: Districts with higher social capital will experience lower levels of crime, whereas districts with lower levels of social capital will experience (ceteris paribus) higher levels of crime. 
Performing various statistical analysis and obtaining all relevant control variables, we expect high internal validity of the results. Nevertheless the external validity of the results might prove low: Neither can we determine whether these results hold for other time periods in Germany, nor can we extrapolate these results to other regions. However external validity can be argued for, if these results prove to be in line with research that has been conducted in other regions and other time periods.

## Bibliography
